### 2012-09-22 sermons/Luke9:23-26.tex
More sermon.

\ldots and follow Me.
\I  The conditions must be met before salvation and discipleship start.

\subsection{The principle}
For whoever desires to save his life will lost it, \ldots
\I  Note that no one can actually save their own life, 
        they can only desire/attempt to.

\ldots but whoever loses his life for My sake will save it.
\I  It must be for His sake!

>>>>

\I  ``\ldots and follow Me.''
\BI \I  These terms are universal. 
        No one gets into God's kingdom without first submitting to these terms. 
    \I  They are Jesus' prerequisite to becoming His disciple.
    \I  And these are the terms you agreed to when 
            God saved you and imputed His Son's righteousness on your behalf
            if you are a true disciple of the Lord Jesus Christ. \EI

\subsection{The disciple's treasure}
\I  Now you may be wondering where the good news is,
        and it is in verse 24.
\Q{ For whoever desires to save his life will lose it,
    but whoever loses his life for My sake will save it.}
\I  ``For'' means that Jesus is explaining the previous verse.
    He is giving the principle that undergirds verse 23.
\I  He explains this principle from both a negative and positive
        perspective.
\I  Jesus starts with the negative,
    ``For whoever desires to save his life will lose it,''
\BI \I  This is the one who was unwilling to surrender his life 
            to serve Jesus.
    \I  Instead, he desired to save it, 
    \EI

\I  Note that no one can actually save their own life, 
        they can only desire/attempt to.

\I  It must be for His sake!
